---
title: "SAT Analysis"
author: "Mika Asaba (masaba@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_float: true
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

Libraries.
```{r echo=FALSE, message=FALSE}
rm(list=ls())

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)

library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(readxl)
library(here)
library(janitor)
library(viridis)
```

Experiment 1
----------------------------------------
Read in file.
```{r, message=FALSE}
exp1.raw = read_excel("../data/ODT_data.xlsx",sheet=2)
```


Clean file.
```{r}
exp1.clean = exp1.raw %>%
  mutate(memory_correct = ifelse((condition == "Better" & memory == "good") | condition == "Worse" & memory == "bad", TRUE, FALSE),
         chose_drawing = choice == "drawing")
```

Filter subjects.
```{r}
exp1.filt = exp1.clean %>%
  filter(memory_correct == TRUE, warmup == "good", include == "y")

exp1.filt.4 = filter(exp1.filt, age >= 4, age < 5)

exp1.all = exp1.clean %>%
  filter(warmup == "good", include == "y")

exp1.best.self.filt = exp1.filt %>%
  filter(condition == "Better", self_evaluation_best == "own")

exp1.worst.self.filt = exp1.filt %>%
  filter(condition == "Worse", self_evaluation_worst == "bad")

exp1.self.middle = full_join(exp1.best.self.filt, exp1.worst.self.filt)

exp1.yoked.best = exp1.filt %>%
  filter(condition == "Better", yoked_evaluation_best == "good")

exp1.yoked.best = exp1.filt %>%
  filter(condition == "Better", yoked_evaluation_best == "good")

exp1.yoked.worst = exp1.filt %>%
  filter(condition == "Worse", yoked_evaluation_worst == "bad")

exp1.yoked.middle = full_join(exp1.yoked.best, exp1.yoked.worst)

#exp1.filt.bestcorr = exp1.clean %>%
 # filter(memory_correct == TRUE, warmup == "good", include == "y", self_evaluation_best == "good")
```

Tidy data.
```{r}
exp1.evaluations = exp1.filt %>%
  select(video_id, age, age_bin, condition,other_evaluation_best, other_evaluation_worst, self_evaluation_best, self_evaluation_worst) %>%
  gather("other_self","evaluation", other_evaluation_best,other_evaluation_worst, self_evaluation_best, self_evaluation_worst) %>%
  mutate(best_worst = other_self,
         other_self = str_sub(other_self,1,4),
         other_self = factor(other_self, levels=c("othe","self"),labels=c("other","self")),
         best_worst = str_sub(best_worst,-4),
         best_worst = factor(best_worst, levels=c("best","orst"),labels=c("best","worst")))

exp1.evaluations.filt = exp1.filt.bestcorr %>%
  select(video_id, age, age_bin, condition,other_evaluation_best, other_evaluation_worst, self_evaluation_best, self_evaluation_worst) %>%
 # filter(self_evaluation_best == "good") %>%
  gather("other_self","evaluation", other_evaluation_best,other_evaluation_worst, self_evaluation_best, self_evaluation_worst) %>%
  mutate(best_worst = other_self,
         other_self = str_sub(other_self,1,4),
         other_self = factor(other_self, levels=c("othe","self"),labels=c("other","self")),
         best_worst = str_sub(best_worst,-4),
         best_worst = factor(best_worst, levels=c("best","orst"),labels=c("best","worst")))
```

### Demographics
```{r}
exp1.dems = exp1.filt %>%
  summarise(num_age = n(),
            avg_age = mean(age),
            sd_age = sd(age),
            min_age = min(age),
            max_age = max(age))
exp1.dems
```

### Counterbalancing
```{r}
table(exp1.filt$condition, exp1.filt$age_bin)
```


### Plots

Primary DV: Blocks or drawing?
```{r}
# Table w/ means and CIs
exp1.means = exp1.filt %>%
  group_by(condition) %>%
  multi_boot_standard(col = "chose_drawing") 
exp1.means

# Table w/ counts and means
exp1.counts = exp1.filt %>%
  group_by(condition,chose_drawing) %>%
  summarise(n = n()) %>%
  mutate(freq = n/sum(n))
exp1.counts

#Plot color
ggplot() + 
  geom_bar(data=exp1.counts, aes(x = factor(condition), y = freq, fill=chose_drawing), stat="identity",width=.5) + 
  geom_linerange(data = exp1.means, mapping=aes(x = factor(condition), ymin = ci_lower, ymax = ci_upper))+
  xlab("") + 
  ylab("Choice of Tasks") +
  geom_hline(yintercept=.5, linetype="dotted") +
  ylim(0,1) +
  theme(text = element_text(size=20)) +
  theme_minimal() +
  scale_fill_manual(values=c("lightsteelblue2","#0072B2"))
#  guides(fill=FALSE)


# Table w/ means and CIs
exp1.means = exp1.filt %>%
  group_by(age_bin,condition) %>%
  multi_boot_standard(col = "chose_drawing") 
exp1.means

# Table w/ counts and means
exp1.counts = exp1.filt %>%
  group_by(age_bin,condition,chose_drawing) %>%
  summarise(n = n()) %>%
  mutate(freq = n/sum(n))
exp1.counts

#Plot color
ggplot() + 
  geom_bar(data=exp1.counts, aes(x = factor(condition), y = freq, fill=chose_drawing), stat="identity",width=.5) + 
  geom_linerange(data = exp1.means, mapping=aes(x = factor(condition), ymin = ci_lower, ymax = ci_upper))+
  xlab("") + 
  ylab("Choice of Tasks") +
  geom_hline(yintercept=.5, linetype="dotted") +
  ylim(0,1) +
  theme(text = element_text(size=20)) +
  theme_minimal() +
  scale_fill_manual(values=c("lightsteelblue2","#0072B2")) +
  facet_grid(~ age_bin)
  #guides(fill=FALSE)
```

FILTERING KIDS WHO RATED THEMSELVES AS IN THE MIDDLE
```{r}
exp1.dems = exp1.self.middle%>%
  group_by(age_bin) %>%
  summarise(num_age = n(),
            avg_age = mean(age),
            sd_age = sd(age),
            min_age = min(age),
            max_age = max(age))
exp1.dems

exp1.means = exp1.self.middle %>%
  group_by(condition) %>%
  multi_boot_standard(col = "chose_drawing") 
exp1.means

# Table w/ counts and means
exp1.counts = exp1.self.middle %>%
  group_by(condition,chose_drawing) %>%
  summarise(n = n()) %>%
  mutate(freq = n/sum(n))
exp1.counts

#Plot color
ggplot() + 
  geom_bar(data=exp1.counts, aes(x = factor(condition), y = freq, fill=chose_drawing), stat="identity",width=.5) + 
  geom_linerange(data = exp1.means, mapping=aes(x = factor(condition), ymin = ci_lower, ymax = ci_upper))+
  xlab("") + 
  ylab("Choice of Tasks") +
  geom_hline(yintercept=.5, linetype="dotted") +
  ylim(0,1) +
 # guides(fill=guide_legend(title=NULL)) +
  theme(text = element_text(size=20)) +
  theme_few() +
  scale_fill_manual(values=c("lightsteelblue2","#0072B2"))
```

FILTERING KIDS WHO OTHERS RATED AS IN THE MIDDLE
```{r}
exp1.dems = exp1.yoked.middle%>%
  group_by(age_bin) %>%
  summarise(num_age = n(),
            avg_age = mean(age),
            sd_age = sd(age),
            min_age = min(age),
            max_age = max(age))
exp1.dems

exp1.means = exp1.yoked.middle %>%
  group_by(age_bin,condition) %>%
  multi_boot_standard(col = "chose_drawing") 
exp1.means

# Table w/ counts and means
exp1.counts = exp1.yoked.middle %>%
  group_by(condition,chose_drawing) %>%
  summarise(n = n()) %>%
  mutate(freq = n/sum(n))
exp1.counts

#Plot color
ggplot() + 
  geom_bar(data=exp1.counts, aes(x = factor(condition), y = freq, fill=chose_drawing), stat="identity",width=.5) + 
  geom_linerange(data = exp1.means, mapping=aes(x = factor(condition), ymin = ci_lower, ymax = ci_upper))+
  xlab("") + 
  ylab("Choice of Tasks") +
  geom_hline(yintercept=.5, linetype="dotted") +
  ylim(0,1) +
 # guides(fill=guide_legend(title=NULL)) +
  theme(text = element_text(size=20)) +
  theme_few() +
  scale_fill_manual(values=c("lightsteelblue2","#0072B2")) +
  facet_grid(~ age_bin)
```

Evaluation questions.
```{r}
#filter kids who said that the best drawing was the best in the other condition

exp1.evaluations.filt = filter(exp1.evaluations, best_worst == "best" & evaluation == "good")

ggplot() + 
  geom_bar(data=exp1.evaluations, aes(x = factor(best_worst), fill=evaluation), width=.5) +
  theme_few() +
  scale_color_viridis() +
  facet_grid(~ other_self)

ggplot() + 
  geom_bar(data=exp1.evaluations.filt, aes(x = factor(best_worst), fill=evaluation), width=.5) +
  facet_grid(~ other_self) +
  theme_few() +
  scale_color_viridis() +
  facet_grid(other_self~ age_bin)



```

### Analyses
Mixed-effects model
```{r}
summary(glm(chose_drawing ~ condition + age,
               data = exp1.filt, 
               family = "binomial"))

summary(glm(chose_drawing ~ condition + age,
               data = exp1.self.middle, 
               family = "binomial"))

summary(glm(chose_drawing ~ condition + age,
               data = exp1.yoked.middle, 
               family = "binomial"))
```

Fisher's Exact
```{r}
#make table with counts of children who chose fail and success confederates
exp1.n = exp1.filt %>%
  group_by(condition) %>%
  summarise(num_chose_drawing = sum(chose_drawing),
            num_chose_blocks = n() - sum(chose_drawing))
exp1.n

#remove condition column
exp1.fisher = select(exp1.n, num_chose_drawing, num_chose_blocks)

#run test
fisher.test(exp1.fisher)

#make table with counts of children who chose fail and success confederates
exp1.n = exp1.filt.4 %>%
  group_by(condition) %>%
  summarise(num_chose_drawing = sum(chose_drawing),
            num_chose_blocks = n() - sum(chose_drawing))
exp1.n

#remove condition column
exp1.fisher = select(exp1.n, num_chose_drawing, num_chose_blocks)

#run test
fisher.test(exp1.fisher)
```


Binomial Tests
```{r}
#Better Condition
binom.test(exp1.n$num_chose_drawing[1], exp1.n$num_chose_drawing[1] + exp1.n$num_chose_blocks[1])

#Worse Condition
binom.test(exp1.n$num_chose_drawing[2], exp1.n$num_chose_drawing[2] + exp1.n$num_chose_blocks[2])
```


Future conditions to run: 
1. "Worse" Worse condition: have 3 yr olds draw their friend's face (i.e., something easier than a tree)
2. Control for Better condition: children are not just threatened -- if the better drawing is the experimenter, then they might choose drawing more often
3. Make children choose to draw even when the experimenter has an inflated belief about them (i.e., when they don't want to make their friend feel bad, or when the experimenter can teach them about drawing)


